---
title: "Trading Strategy"
output: html_notebook
---
The purpose of this notebook is to use statistic and plotting packages on the 
explosive_data_clean.csv file to uncover patterns that might help establish
a profitable trading strategy. For a definition of column attributes please 
reference the attached READ ME in the Git Hub repository.

I begin by importing tha packages I will use. Then I import the dataset and
assign it to the variable 'data'
```{r}
library(tidyverse)
library(lmtest)
data = read.csv('explosive_data_clean.csv', header = TRUE)
head(data)
```
Notice that all columns have been cast as character even though they are 
intended to be numeric. For data I wish to run functions on I will need to 
convert to numeric data types.
```{r}
data$three_day_return <- as.numeric(as.character(data$three_day_return))
data$daily_increase <- as.numeric(as.double(data$daily_increase))
data$short_percent <- as.numeric(as.double(data$short_percent))
```



I want to start by looking at three_day_return based on rsi and flag color. 
```{r}
ggplot(
   data = data,
  mapping = aes(x = three_day_return, y = rsi)
) + geom_point(mapping = aes(color = flag)
) +  scale_color_manual(values = c("B" = "blue", "G" = "green",
                                     'P' = "purple", "R" = 'red', 
                                     'Y' = 'yellow')
) + geom_vline(xintercept = 0, linetype = 'solid', color = 'black')
```
Things that stand out from this plot..

1) Red flag trades are all less than 55 RSI and there are significantly more
losers than winners.

2) There were the same number of purple winners and losers and the winner on 
average won more than the losers.

3) Blue flags appear to have a moderate negative correlation with profits where
a higher RSI yields lagrer losses.

4) There appears to be the presence of heteroscedasticity in the data, where as
RSI increases the variance of profit and loss becomes greater.

Now I will run some basic commands to quantify and verify my visual.
observations.
```{r}
R_flag_data <- filter(data, flag == 'R')
R_flag_winners <- filter(R_flag_data, three_day_return > 0.0)
R_flag_losers <- filter(R_flag_data, three_day_return < 0.0)

P_flag_data <- filter(data, flag == 'P')
P_flag_winners <- filter(P_flag_data, three_day_return > 0.0)
P_flag_losers <- filter(P_flag_data, three_day_return < 0.0)
P_avg_winner <- round(mean(P_flag_winners$three_day_return))
P_avg_loser <- round(mean(P_flag_losers$three_day_return))

B_flag_data <- filter(data, flag == 'B')
cor(B_flag_data$rsi, B_flag_data$three_day_return, use = "complete.obs")

model <- lm(rsi ~ three_day_return, data = data)
breusch_pagan_test <-bptest(model)
breusch_pagan_test
```

The results from this analysis shows that..


1) There are in fact 7 Winners and 13 losers under the red flags

2) There were 11 and 11 respectivly with the winner 
returning a mean profit of 12% and losers returning a mean loss of 7%.

3) There is in fact a -.38 correlation between RSI and three_day_returns for
blue flags.

4) The Breusch-Pagan test return a BP statistic of .13 and a P-value of .71
which is not significant. There is not strong evidence of the presence of
heteroscedasticity in the data.


Next I want to see how daily_increase impacts three_day_return.
```{r}
ggplot(
   data = data,
  mapping = aes(x = three_day_return, y = daily_increase)
) + geom_point(mapping = aes(color = flag)
) +  scale_color_manual(values = c("B" = "blue", "G" = "green",
                                     'P' = "purple", "R" = 'red', 
                                     'Y' = 'yellow')
) 
```

Just by looking at this graph it appears that avoiding trades with a
daily_increase greater than 50 eliminates 6 losers while keeping nearly all of
my largest winners.


Finally, I want to look at how short_percent impacts three_day_return.
```{r}
ggplot(
   data = data,
  mapping = aes(x = three_day_return, y = short_percent)
) + geom_point(mapping = aes(color = flag)
) +  scale_color_manual(values = c("B" = "blue", "G" = "green",
                                     'P' = "purple", "R" = 'red', 
                                     'Y' = 'yellow')
) 
```
Looking at this graph I can see that avoiding trades in stocks that are shorted 
more than 20% will remove 7 losers and only 1 winner. 


Based off the information I have gathered from this analysis I want to begin 
formulating my strategy. 

--I will only take trades that are above 55 RSI.

--I will only take trades with a short % less than 20.

--I will only take trades that have a daily increase of less than 50%.

--I will only hold trades for three days and sell at the close of the third day.


Applying these limitations to the data my theoretical strategy will yield...

37 Winners and 51 Losers with a win percent of 42%

Average profit of 17.2% 

Average loss of 9%

Total Profit 636.9%

Total Loss 458.9%

A Net Profit of 178%
```{r}
rsi_filter <- filter(data, rsi > 55)
short_per_filter <- filter(rsi_filter, short_percent < 20)
strategy <- filter(short_per_filter, daily_increase < 50)

num_winner <- sum(strategy$three_day_return > 0)
win_avg_per <- mean(strategy$three_day_return[strategy$three_day_return > 0])
total_profit <- sum(strategy$three_day_return[strategy$three_day_return > 0])

num_loser <- sum(strategy$three_day_return < 0)
loss_avg_per <- mean(strategy$three_day_return[strategy$three_day_return < 0])
total_loss <- sum(strategy$three_day_return[strategy$three_day_return < 0])

hist(strategy$three_day_return,breaks = 10)
boxplot(strategy$three_day_return[strategy$three_day_return > 0])
```
ggplo



